---
title: "Elections project"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache = TRUE)
library(readr)
library(purrr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(gmodels)
library(Sleuth3)
library(GGally)
library(tidyverse)
library(tidymodels)
library(readxl)
```

::: {.callout-tip collapse="true" icon="true"}
# Introduction to my project
* For my final project in STAT 244-SC (spring 2025) I chose to analyze the correlation between female population and voter turnout in 2016 across 32 counties in New Mexico. For this project, I am working with the _County Presidential Election Returns 2000-2020 (Version V13)_ dataset collected by the MIT Election Data and Science Lab. My goal is to determine whether there is an increase in voter turnout when the population of women in a county is high. 
:::

```{r}
election <- read.csv("Election.csv")
nm_election <- election %>% filter(state == "New Mexico")
```

```{r echo=FALSE}
nm_election <- rename(nm_election, tp = `total_population`)
nm_election <- rename(nm_election, vt16 = `voterturnout16_pct`)
nm_election <- rename(nm_election, f = `female_pct`)
```

```{r}
nm_election %>%
    ggplot(aes(x = vt16)) +
    geom_histogram(fill = "maroon1", color = "black", bins = 30) + 
    labs(title = "Voter Turnout Distribution (2016)", 
         x = "Percentage of Voter Turnout in 2016", 
         y = "Frequency") +
    theme_classic()
nm_election %>%
    ggplot(aes(x = vt16)) +
    geom_boxplot(fill = "maroon1", color = "black") + 
    labs(title = "Boxplot of Voter Turnout (2016)", 
         x = "Percentage of Voter Turnout in 2016", 
         y = "Frequency") +
    theme_classic()
```
